Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-10-21 2016-Weak-FH-Bisim/WeakBisim.tex
Example code in Appendix

\usepackage[T1]{fontenc}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{DotArrow}
\usepackage{hyperref}

@@

Let us start with the basic version, with no error counter.

@@

>>>>

\usepackage[T1]{fontenc}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{DotArrow}
\usepackage{hyperref}
\usepackage{listings}
\lstset{basicstyle=\small}

@@

@@

The first piece of code is the textual definition of the SimpleProtSec
pNet. This code should be intuitive enough to read, with the following
conventions:

\begin{itemize}
  \item Constants of any type (including Action) must be declared as
    ``const''. They are used either as functions with argument, as
    typically \texttt{in(msg)}, or constants without argument, denoted
    as \texttt{\$tau}. Identifiers without the ``?'' marker are
    variables.
  \item Variables can be declared either: inside a pLTS state (normal
    state variable), as global variable of a pLTS (see e.g. ...), or
    as an input variable in a transition, as \texttt{?msg} in pLTS M1
    here.
  \item \TODO{continue...}
\end{itemize}

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
SimpleProtSpec2:
import "Data_Alg.algp"
root SimpleProtSpec2
const in, out:Action
const p_send, q_recv: Action
const tau:Action

pLTS M1
initial a0
vars ?msg:Data

state a0
transition in(msg) -> a1 {a1_msg:=msg}

state a1
vars a1_msg:Data {m1_c:=0}:Int

transition out(a1_msg, m1_c) -> a0
transition synchro($tau)  -> a1 {m1_c:=m1_c+1}

pNet SimpleProtSpec2
holes P,Q
subnets P,M1,Q
vars p_a,q_a:Action m:Data c:Int

vector SV0 <p_send(m), in(m),_>->p_send(m)
vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
vector SV2 <_, out(m,c), q_recv(m)>->q_recv(m,c)
vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m)]

  \end{lstlisting}

The corresponding generated Open Automaton was given in Figure \ref{},
page \pageref{}.

Next is the code for the SimpleProtImpl pNet:

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
SimpleProtImpl:
import "Data_Alg.algp"

root SimpleProtImpl2

const in,out:Action
const tau,p_send,q_recv,m_recv,m_send,m_error: Action
const s_send,s_ack,s_error,r_recv,r_ack: Action

pLTS M1
initial a0
vars ?msg:Data ?c:Int

state a0
transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_c:=c}

state a1
vars a1_msg:Data a1_c:Int
transition m_send(a1_msg, a1_c) -> a0 
transition synchro($tau) -> a2

state a2
transition $m_error -> a0

pLTS Sender
initial s0
vars ?msg:Data

state s0
transition in(msg) -> s1 {s1_msg:=msg, s1_c:=0}

state s1
vars s1_msg:Data s1_c:Int
transition s_send(s1_msg, s1_c) -> s2

state s2
vars  s2_c:Int
transition $s_ack -> s0
transition $s_error -> s1 {s1_c:=s2_c+1}

pLTS Receiver
initial r0
vars ?msg:Data ?c:Int

state r0
transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_c:=c}

state r1
vars r1_msg:Data r1_c:Int
transition out(r1_msg, r1_c) -> r2

state r2
transition $r_ack -> r0

pNet medium
subnets Sender, M1, Receiver
vars m:Data c:Int
vector SV0 <in(m), _, _>->in(m)
vector SV1 <s_send(m,c), m_recv(m,c), _>->synchro($tau)
vector SV2 <_, m_send(m), r_recv(m)>->synchro($tau)
vector SV3 <$s_ack, _, $r_ack>->synchro($tau)
vector SV4 <$s_error, $m_error, _>->synchro($tau)
vector SV5 <_, _, out(m,c)>->out(m,c)

pNet SimpleProtImpl2
holes P,Q
subnets P,medium,Q
vars p_a,q_a:Action  m:Data c:Int
vector SV0 <p_send(m), in(m),_>->in(m)
vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
vector SV2 <_, out(m,c), q_recv(m,c)>->out(m,c)
vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m,c)]
\end{lstlisting}

From this code,A more compact view (maybe more readable ???) is given
by the pretty-printer of VerCors:

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
SimpleProtImpl2
--------------------
SV6 SVs: <p_send(m), in(m), _>-->in(m)
SV7 SVs: <p_a, _, _>-->p_a, p_a!=(p_send(m))
SV8 SVs: <_, out(m, c), q_recv(m, c)>-->out(m, c)
SV9 SVs: <_, _, q_a>-->q_a, q_a!=(q_recv(m, c))
SV11 SVs: <_, _tau_, _>-->_tau_
SV12 SVs: <_, _tau_, _>-->_tau_
SV13 SVs: <_, _tau_, _>-->_tau_
SV14 SVs: <_, _tau_, _>-->_tau_
SV15 SVs: <_, _tau_, _>-->_tau_
Holes: P
Subnets: medium
- medium
- SV0 SVs: <in(m), _, _>-->in(m)
- SV1 SVs: <s_send(m, c), m_recv(m, c), _>-->_tau_
- SV2 SVs: <_, m_send(m), r_recv(m)>-->_tau_
- SV3 SVs: <s_ack, _, r_ack>-->_tau_
- SV4 SVs: <s_error, m_error, _>-->_tau_
- SV5 SVs: <_, _, out(m, c)>-->out(m, c)
- SV10 SVs: <_, _tau_, _>-->_tau_
- pLTS: Sender
- - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_c := 0}
- - Transition: s1---s_send(s1_msg, s1_c)-->s2, {}
- - Transition: s2---s_ack-->s0, {}
- - Transition: s2---s_error-->s1, { s1_c := s2_c+1}
- - Variable: s1_c, State: s1, Value(s) = 0,s2_c+1,
- - Variable: s1_msg, State: s1, Value(s) = msg,
- pLTS: M1
- - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_c := c}
- - Transition: a1---m_send(a1_msg, a1_c)-->a0, {}
- - Transition: a1---_tau_-->a2, {}
- - Transition: a2---m_error-->a0, {}
- - Variable: a1_msg, State: a1, Value(s) = msg,
- - Variable: a1_c, State: a1, Value(s) = c,
- pLTS: Receiver
- - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_c := c}
- - Transition: r1---out(r1_msg, r1_c)-->r2, {}
- - Transition: r2---r_ack-->r0, {}
- - Variable: r1_msg, State: r1, Value(s) = msg,
- - Variable: r1_c, State: r1, Value(s) = c,
Holes: Q
\end{lstlisting}

Finaly, we list here, in raw format, the 24 OTs computed by the tool:

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
INFO  SimpleProtImpl2 - Total: 24 OTs
INFO  SimpleProtImpl2 - 
		{P|->p_send(m:sva_SV6:1:1)},   [((in(msg))=:ra:Sender:121:1)/\(:ra:Sender:121:1=(in(m:sva_SV0:12:1)))/\((in(m:sva_SV0:12:1))=(in(m:sva_SV6:1:1)))],   {s1_msg := msg, s1_c := 0}
	OT:1 ------------------------------------------------------------
		<s0_a0_r0>-----in(m:sva_SV6:1:1)----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:2 ------------------------------------------------------------
		<s0_a0_r0>-----p_a:sva_SV7:1:2----><s0_a0_r0>

INFO  SimpleProtImpl2 - 
		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:3 ------------------------------------------------------------
		<s0_a0_r0>-----q_a:sva_SV9:1:4----><s0_a0_r0>

INFO  SimpleProtImpl2 - 
		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:4 ------------------------------------------------------------
		<s1_a0_r0>-----p_a:sva_SV7:1:2----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:5 ------------------------------------------------------------
		<s1_a0_r0>-----q_a:sva_SV9:1:4----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1144:1)/\(:ra:Sender:1144:1=(s_send(m:sva_SV1:114:2, c:sva_SV1:114:2)))/\((m_recv(msg, c))=:ra:M1:1145:1)/\(:ra:M1:1145:1=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
	OT:6 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1174:1)/\(:ra:Sender:1174:1=(s_send(m:sva_SV1:117:2, c:sva_SV1:117:2)))/\((m_recv(msg, c))=:ra:M1:1175:1)/\(:ra:M1:1175:1=(m_recv(m:sva_SV1:117:2, c:sva_SV1:117:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
	OT:7 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1204:1)/\(:ra:Sender:1204:1=(s_send(m:sva_SV1:120:2, c:sva_SV1:120:2)))/\((m_recv(msg, c))=:ra:M1:1205:1)/\(:ra:M1:1205:1=(m_recv(m:sva_SV1:120:2, c:sva_SV1:120:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
	OT:8 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1234:1)/\(:ra:Sender:1234:1=(s_send(m:sva_SV1:123:2, c:sva_SV1:123:2)))/\((m_recv(msg, c))=:ra:M1:1235:1)/\(:ra:M1:1235:1=(m_recv(m:sva_SV1:123:2, c:sva_SV1:123:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
	OT:9 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1264:1)/\(:ra:Sender:1264:1=(s_send(m:sva_SV1:126:2, c:sva_SV1:126:2)))/\((m_recv(msg, c))=:ra:M1:1265:1)/\(:ra:M1:1265:1=(m_recv(m:sva_SV1:126:2, c:sva_SV1:126:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
	OT:10 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:11 ------------------------------------------------------------
		<s2_a1_r0>-----p_a:sva_SV7:1:2----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:12 ------------------------------------------------------------
		<s2_a1_r0>-----q_a:sva_SV9:1:4----><s2_a1_r0>

INFO  SimpleProtImpl2 - 
		{},   [(_tau_=:ra:M1:11420:1)/\(:ra:M1:11420:1=_tau_)/\(_tau_=_tau_)],   {}
	OT:13 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{},   [(_tau_=:ra:M1:11720:1)/\(:ra:M1:11720:1=_tau_)/\(_tau_=_tau_)],   {}
	OT:14 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{},   [(_tau_=:ra:M1:12020:1)/\(:ra:M1:12020:1=_tau_)/\(_tau_=_tau_)],   {}
	OT:15 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{},   [(_tau_=:ra:M1:12320:1)/\(:ra:M1:12320:1=_tau_)/\(_tau_=_tau_)],   {}
	OT:16 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{},   [(_tau_=:ra:M1:12620:1)/\(:ra:M1:12620:1=_tau_)/\(_tau_=_tau_)],   {}
	OT:17 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
	OT:18 ------------------------------------------------------------
		<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
	OT:19 ------------------------------------------------------------
		<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>

INFO  SimpleProtImpl2 - 
		{},   [(s_error=:ra:Sender:11413:1)/\(:ra:Sender:11413:1=s_error)/\(m_error=:ra:M1:11414:1)/\(:ra:M1:11414:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
	OT:20 ------------------------------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
		{},   [(s_error=:ra:Sender:11713:1)/\(:ra:Sender:11713:1=s_error)/\(m_error=:ra:M1:11714:1)/\(:ra:M1:11714:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
	OT:21 ------------------------------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
		{},   [(s_error=:ra:Sender:12013:1)/\(:ra:Sender:12013:1=s_error)/\(m_error=:ra:M1:12014:1)/\(:ra:M1:12014:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
	OT:22 ------------------------------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
		{},   [(s_error=:ra:Sender:12313:1)/\(:ra:Sender:12313:1=s_error)/\(m_error=:ra:M1:12314:1)/\(:ra:M1:12314:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
	OT:23 ------------------------------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

INFO  SimpleProtImpl2 - 
		{},   [(s_error=:ra:Sender:12613:1)/\(:ra:Sender:12613:1=s_error)/\(m_error=:ra:M1:12614:1)/\(:ra:M1:12614:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
	OT:24 ------------------------------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

INFO  SimpleProtImpl2 - Total: 24 SATISFIABLE OTs
INFO  SimpleProtImpl2 -        278 UNSATISFIABLE OTs
INFO  SimpleProtImpl2 - Total Time: 1056 ms

\end{lstlisting}
